\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-13 doc/paper.tex
final, please be no typos please be no typos

\usepackage{xspace}
\usepackage{subfigure}
\usepackage{url}
\usepackage{hyperref}

@@

	% author names and affiliations
	% use a multiple column layout for up to three different
	% affiliations
	\author{ \IEEEauthorblockN{Justin Middleton and Emerson Murphy-Hill}
		\IEEEauthorblockA{North Carolina State University, Raleigh, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}

@@

		\item [1] \textbf{Unbiased Exploration} First, provide an interactive
		environment for free exploration. There are a lot of data in some of these
		spreadsheet corpora, and the user should be able to pick for themselves which
		to explore while ignoring the rest. Second, avoid judgments about good and bad
		design. Though users may certainly approach the tool with the intention of
		exploring particular formulae, a formula visualization tool will not
		prioritize any on metrics of good or bad practice.

@@

	\begin{figure*}[t] \centering \includegraphics[width=0.8\textwidth]{IFargslabel}
		\caption{A picture of \toolname displaying the common arguments to the \texttt{IF}
			function's first parameter} \centering \label{fig:fullpic} \end{figure*}

@@

	In balancing this chosen form with the goals in Section~\ref{goals}, we faced a
	number of decisions in how to visualize the data. Below, we've outlined those
	that had the largest impact in the values that appear in the tree.
	\begin{itemize}

@@

		\ \ For example, in the pictured \texttt{IF} function, we found that people
		often use another \texttt{IF} statement as the second or third arguments of
		the top-level \texttt{IF}. If we only consider functions exactly where they're
		found embedded in the formula, then information about the same function --
		\texttt{IF}, in this case -- will be scattered across different trees with no
		way to aggregate them and see, for example, how many times \texttt{IF} was
		used overall. If we record every instance of a function by ignoring their
		context -- that is, including an \texttt{IF} embedded within a \texttt{SUM}
		function in the same node as the top-level \texttt{IF} -- then the tool will
		represent some functions in multiple redundant nodes to capture every possible
		level of nesting. For now, we only include the first, with the latter to be
		added as an option in the future.

@@

	%Lookup example
	For a deeper example, the LOOKUP functions are some of the most popular in
	Excel yet come with a number of important but silent requirements for proper
	use, and, as such, they have warranted some extra attention with regards to
	spreadsheet design. In short, these functions are for ``when you need to look
	in a single row or column and find a value from the same position in a second
	row or
	column"\footnote{\href{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}}. Examples of their use can be found in Figure~\ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.

	\begin{figure}[h] \centering
		\includegraphics[width=.5\textwidth]{lookupexample} \caption{Demonstrations of
			LOOKUP and VLOOKUP} \label{fig:lookupexample} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
			three arguments}  \label{fig:lookups} \end{figure}

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
		\includegraphics[width=.5\textwidth]{hlookup} \caption{VLOOKUP and HLOOKUP with
			four arguments} \label{fig:vhlookups}\end{figure}

@@

		\begin{wrapfigure}{O}{.25\textwidth} \centering
			\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
				in SUM, which was a commonly noted smell in the user study} \label{fig:sum}
		\end{wrapfigure}

@@

	\subsection{Use in Education} Users found \toolname's inclusion of examples to
	be especially useful since none of the them considered themselves to be experts
	of Excel, their self-reported proficiencies ranging from ``fairly familiar"
	(P2) to ``not extremely familiar" (P4). For example, as P1 explored the \texttt{VLOOKUP}
	function, they said they could use the tool to collect more examples than the
	documentation offers even though they knew the documentation more verbosely
	explained its function signature. Furthermore, in the process of exploring
	trees, P1 and P3 also gravitated towards some functions they had not used
	before, such as \texttt{PV} and \texttt{IPMT}, looking for new features in Excel to explore and
	learn.

@@

	\begin{figure} \centering \includegraphics[width=.4\textwidth]{index}
		\caption{A difficult question: how often is MATCH used in both the second and
			third arguments?} \label{fig:index} \end{figure}

>>>>

\usepackage{xspace}
\usepackage{subfigure}
\usepackage{url}
\usepackage[bookmarks=false]{hyperref}

@@

	% author names and affiliations
	% use a multiple column layout for up to three different
	% affiliations
	\author{ \IEEEauthorblockN{Justin Middleton and Emerson Murphy-Hill}
		\IEEEauthorblockA{North Carolina State University\\Raleigh, North Carolina, USA\\ jamiddl2@ncsu.edu, emerson@csc.ncsu.edu }}

@@

		\item [1] \textbf{Unbiased Exploration} First, provide an interactive
		environment for free exploration. There are a lot of data in some of these
		spreadsheet corpora, and the user should be able to pick for themselves which
		to explore while ignoring the rest. Second, avoid judgments about good and bad
		design. Though users may certainly approach the tool with the intention of
		exploring particular formulae, our formula visualization tool will not
		prioritize any on metrics of good or bad practice.

@@

	\begin{figure*}[t] \centering \includegraphics[width=0.8\textwidth]{IFargslabel}
		\caption{\toolname displaying the common arguments to the \texttt{IF}
			function's first parameter} \centering \label{fig:fullpic} \end{figure*}

@@

	In balancing this chosen form with the goals in Section~\ref{goals}, we faced a
	number of decisions in how to visualize the data. Below, we have outlined those
	that had the largest impact in the values that appear in the tree.
	\begin{itemize}

@@

		\ \ For example, in the pictured \texttt{IF} function, we found that people
		often use another \texttt{IF} statement as the second or third arguments of
		the top-level \texttt{IF}. If we only consider functions exactly where they are
		found embedded in the formula, then information about the same function --
		\texttt{IF}, in this case -- will be scattered across different trees with no
		way to aggregate them and see, for example, how many times \texttt{IF} was
		used overall. If we record every instance of a function by ignoring their
		context -- that is, including an \texttt{IF} embedded within a \texttt{SUM}
		function in the same node as the top-level \texttt{IF} -- then the tool will
		represent some functions in multiple redundant nodes to capture every possible
		level of nesting. For now, we only include the first, with the latter to be
		added as an option in the future.

@@

	%Lookup example
	For a deeper example, the \texttt{LOOKUP} functions are some of the most popular in
	Excel yet come with a number of important but silent requirements for proper
	use, and, as such, they have warranted some extra attention with regards to
	spreadsheet design. In short, these functions are for ``when you need to look
	in a single row or column and find a value from the same position in a second
	row or
	column"\footnote{\href{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}{https://support.office.com/en-us/article/LOOKUP-function-446d94af-663b-451d-8251-369d5e3864cb}}. Examples of their use can be found in Figure~\ref{fig:lookupexample}, and we will cover each type in more depth to better understand the visualizations for these functions.

	\begin{figure}[h] \centering
		\includegraphics[width=.5\textwidth]{lookupexample} \caption{Demonstrations of
			\texttt{LOOKUP} and \texttt{VLOOKUP}} \label{fig:lookupexample} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
		\includegraphics[width=.5\textwidth]{lookup-3} \caption{\texttt{LOOKUP} with two and
			three arguments}  \label{fig:lookups} \end{figure}

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
		\includegraphics[width=.5\textwidth]{hlookup} \caption{\texttt{VLOOKUP} and \texttt{HLOOKUP} with
			four arguments} \label{fig:vhlookups}\end{figure}

@@

		\begin{wrapfigure}{O}{.25\textwidth} \centering
			\includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters
				in \texttt{SUM}, which was a commonly noted smell in the user study} \label{fig:sum}
		\end{wrapfigure}

@@

	\subsection{Use in Education} Users found \toolname' inclusion of examples to
	be especially useful since none of the them considered themselves to be experts
	of Excel, their self-reported proficiencies ranging from ``fairly familiar"
	(P2) to ``not extremely familiar" (P4). For example, as P1 explored the \texttt{VLOOKUP}
	function, they said they could use the tool to collect more examples than the
	documentation offers even though they knew the documentation more verbosely
	explained its function signature. Furthermore, in the process of exploring
	trees, P1 and P3 also gravitated towards some functions they had not used
	before, such as \texttt{PV} and \texttt{IPMT}, looking for new features in Excel to explore and
	learn.

@@

	\begin{figure} \centering \includegraphics[width=.4\textwidth]{index}
		\caption{A difficult question: how often is \texttt{MATCH} used in both the second and
			third arguments?} \label{fig:index} \end{figure}
